### 2023-11-14 main.tex
check

i.e. the product over sites of multinomial distribution with parameters $\nu=1$ and $p_{a}=\beta_{a}$. This is a direct consequence of the fact that $\beta_{N}=1-(\beta_{1}+\ldots+\beta_{N-1})$. 

@@

where the expectation is take with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 

@@

	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain. This matrix $\mathcal{S}_{1}$ is given by
	\begin{equation}\label{S1-L1}
		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
	\end{equation}
	thus
	\begin{equation}
		\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)(1-\delta_{\mu,N})|N\rangle
	\end{equation}
	By taking the tensor product over the chain we obtain 
	\begin{equation}
		S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
	\end{equation}
	therefore, projecting on $\langle \bm{\tau}|$ we have
	\begin{equation}\label{Tensor-S1}
		\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)
	\end{equation}
	\begin{comment}
		Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
		\begin{equation}
			\begin{split}
				\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
				\\&
				+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\} 
			\end{split}
		\end{equation}
		where we have introduced, $\forall x\in \{1,\ldots,L\}$
		\begin{equation}
			%\eta_{x}=\begin{cases}
				%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
				%	d_{x}\qquad &\text{otherwise}
				%\end{cases}\qquad
				\theta_{x}(b)=\begin{cases}
					\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
					N \qquad &\text{otherwise}
				\end{cases}
			\end{equation}
			The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
			This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
			\begin{align*}
				\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
				\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
				\\&\otimes
				\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
				\\&=
				\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
			\end{align*}
			\begin{comment}

@@

		In the last equality we have used equation \eqref{ABS_1}. 

@@

					=&\sum_{\bm{\sigma}\in \Omega}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\bm{\sigma}|\Psi\rangle\nonumber\\

@@

			As a consequence, by using again the index $\ell$ in the second term, we have that the normalization condition reads

@@

>>>>

i.e. the product over sites of multinomial distribution with parameters $\nu=1$ and $\beta_{a}$. This is a direct consequence of the fact that $\beta_{N}=1-(\beta_{1}+\ldots+\beta_{N-1})$. 

@@

where the expectation is taken with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 

@@

	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain. This matrix $\mathcal{S}_{1}$ is given by
	\begin{equation}\label{S1-L1}
		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
	\end{equation}
	thus
	\begin{equation}
		\mathcal{S}_{1}^{-1}|\sigma\rangle=|\sigma\rangle+(-1)(1-\delta_{\sigma,N})|N\rangle
	\end{equation}
	By taking the tensor product over the chain we obtain 
	\begin{equation}
		S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
	\end{equation}
	therefore, projecting on $\langle \bm{\tau}|$ we have
	\begin{equation}\label{Tensor-S1}
		\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)
	\end{equation}
	\begin{comment}
		Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
		\begin{equation}
			\begin{split}
				\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
				\\&
				+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\} 
			\end{split}
		\end{equation}
		where we have introduced, $\forall x\in \{1,\ldots,L\}$
		\begin{equation}
			%\eta_{x}=\begin{cases}
				%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
				%	d_{x}\qquad &\text{otherwise}
				%\end{cases}\qquad
				\theta_{x}(b)=\begin{cases}
					\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
					N \qquad &\text{otherwise}
				\end{cases}
			\end{equation}
			The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
			This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
			\begin{align*}
				\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
				\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
				\\&\otimes
				\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
				\\&=
				\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
			\end{align*}
			\begin{comment}

@@

		In the second equality we have rewritten the product by introducing the summation over $b$ and introducing the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$. In the last equality we have used equation \eqref{ABS_1}. 

@@

					=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\

@@

			As a consequence we have that the normalization condition reads

@@

and where $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ . \\ \\
